FoRTE baseline

### 2019-07-19 analysis/paper/paper.Rmd
More methods parameter revisions
- Add parameter table
- Tweak text

$$
M_D = \frac{y_1}{1 + \exp\left[y_2 left( \frac{C_k}{C_k^*} \right)\right]}
$$

@@

Three other parameters:

- Fraction of litter carbon that enters the labile (fast) soil carbon pool (`f_labile`)
- Minimum plant height for reproduction (`minimum_height`)
- Soil-plant water conductance, or "water availability factor" (`water_conductance`)

@@

By default, ED-2.2 supports 17 different plant functional types, which divide plant species according to photosynthetic pathway (C3 vs. C4), growth form (grass vs. tree), leaf phenology habit (deciduous vs. evergreen), biome (e.g. temperate vs. tropical), and successional status (e.g. early, mid, late).
However, we limited our simulations to the four plant functional types that have any appreciable presence at UMBS: Early, mid, and late temperate deciduous trees and pines.
The species comprising these plant functional types are shown in Table 2.

Table 2: Plant functional type-species mappings

@@

For each factorial combination of ED-2.2 configurations (described above), we ran 100 ensemble members from 1901 to 2000.
Each ensemble member was initialized from a "near-bare ground" condition: An equal number of seedlings of each plant functional type (see previous section) at the minimum resolvable size.
Driving meteorological data was 6-hourly CRU-NCEP <!-- TODO ref. More here? --> combined with an annual atmospheric CO~2~ record from Law-Dome ice core [@etheridge_1998_historical] and Mauna Loa observatory [@thoning_1989_atmospheric].
Soil texture was set to 92% sand, 7% silt, and 1% clay, per site-level observations in [@gough_2010_wood].
The initial soil moisture profile was set to the average soil moisture profile reported in the UMBS Ameriflux ancillary data (https://ameriflux.lbl.gov/sites/siteinfo/US-UMd).
The entire model execution workflow was conducted using the Predictive Ecosystem Analyzer (PEcAn, www.pecanproject.org).

@@

@@

```{r param-table}
tbl <- readd(param_table)
tbl <- subset(tbl, select = -unit_parsed)
tbl[["ED Name"]] <- sprintf("`%s`", tbl[["ED Name"]])
knitr::kable(tbl, escape = FALSE, caption = paste0(
  "**Table**: Parameter descriptions. ",
  "For additional information, see the ",
  "[ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters)."
))
```

>>>>

$$
M_D = \frac{y_1}{1 + \exp\left[y_2 \left( \frac{C_k}{C_k^*} \right)\right]}
$$

@@

Other parameters:

- Fraction of litter carbon that enters the labile (fast) soil carbon pool (`f_labile`)
- Minimum plant height for reproduction (`minimum_height`)
- Soil-plant water conductance, or "water availability factor" (`water_conductance`)
- C:N ratio in fine roots (`c2n_fineroot`) and leaves (`c2n_leaf`)
- Leaf turnover rate (evergreen-only; `leaf_turnover_rate`)
- Proportion of dispersal that is "global" (`nonlocal_dispersal`) <!-- TODO What is this? Can I drop it from the analysis? -->

The full list of parameters is shown in Table 2.

```{r param-table}
tbl <- readd(param_table)
tbl <- subset(tbl, Ran == "yes", select = c(-unit_parsed, -Ran))
tbl[["ED Name"]] <- sprintf("`%s`", tbl[["ED Name"]])
knitr::kable(tbl, escape = FALSE, caption = paste0(
  "Table 2: Parameter descriptions. ",
  "For additional information, see the ",
  "[ED2 model wiki](https://github.com/EDmodel/ED2/wiki/PFT-parameters)."
))
```

@@

By default, ED-2.2 supports 17 different plant functional types, which divide plant species according to photosynthetic pathway (C3 vs. C4), growth form (grass vs. tree), leaf phenology habit (deciduous vs. evergreen), biome (e.g. temperate vs. tropical), and successional status (e.g. early, mid, late).
However, we limited our simulations to the four plant functional types that have any appreciable presence at UMBS: Early, mid, and late temperate deciduous trees and pines.
The species comprising these plant functional types are shown in Table 3.

Table 3: Plant functional type-species mappings

@@

For each factorial combination of ED-2.2 configurations (described above), we ran 100 ensemble members from 1901 to 2000.
Each ensemble member was initialized from a "near-bare ground" condition: An equal number of seedlings of each plant functional type (see previous section) at the minimum resolvable size.
Driving meteorological data was 6-hourly CRU-NCEP <!-- TODO ref. More here? --> combined with an annual atmospheric CO~2~ record from Law-Dome ice core [@etheridge_1998_historical] and Mauna Loa observatory [@thoning_1989_atmospheric].
Soil texture was set to 92% sand, 7% silt, and 1% clay, per site-level observations in [@gough_2010_wood].
The initial soil moisture profile was set to the average soil moisture profile reported in the UMBS Ameriflux ancillary data (https://ameriflux.lbl.gov/sites/siteinfo/US-UMd).

@@

All analyses for this work were performed using R 3.6 (see "Colophon" for full details).
Code and supporting data for reproducing this analysis are publicly available on the Open Science Framework (OSF) at https://osf.io/dznuf/.

@@
